Add Plant Functional Type (PFT) labels

### 2021-03-29 R/add_plant_functional_type.Rmd
over 95 done

@@

```{r}
# list unique taxon labels, add an empty columns to fill with plant functional type (PFT) and common name labels.
# PFTs of interest: coniferous_forest, deciduous_forest, woody_shrub, grass_herb, and bare_ground.
taxon_pft_lookup <- data.frame(genusSpecies = unique(cleaned_spectra$genusSpecies),
                               commonName = NA,
                               pft = NA)

@@

  else if(genusSpecies == "Acer circinatum"){
    taxon_pft_lookup$pft[i] = "NA " ??? 
    taxon_pft_lookup$commonName[i] = "vine maple"}

@@

  else if(genusSpecies == "Amelanchier laevis"){
    taxon_pft_lookup$pft[i] = "???" ???
    taxon_pft_lookup$commonName[i] = "Allegheny serviceberry"}

  else if(genusSpecies == "Amyris elemifera"){
    taxon_pft_lookup$pft[i] = "???"     ???
    taxon_pft_lookup$commonName[i] = "sea torchwood"}

@@

  else if(genusSpecies == "Bourreria sp."){
    taxon_pft_lookup$pft[i] = "???"   ???
    taxon_pft_lookup$commonName[i] = "strongbark"}

@@

  else if(genusSpecies == "Cercis canadensis"){
    taxon_pft_lookup$pft[i] = "???"   ???
    taxon_pft_lookup$commonName[i] = "eastern redbud"}

@@

  else if(genusSpecies == "Cornus drummondii"){
    taxon_pft_lookup$pft[i] = "???"    ???
    taxon_pft_lookup$commonName[i] = "roughleaf dogwood"}

  else if(genusSpecies == "Cornus florida"){
    taxon_pft_lookup$pft[i] = "???"    ???
    taxon_pft_lookup$commonName[i] = "flowering dogwood"}

@@

  else if(genusSpecies == "Frangula purshiana"){
    taxon_pft_lookup$pft[i] = "???"     ???
    taxon_pft_lookup$commonName[i] = "Cascara buckthorn"}

@@

  else if(genusSpecies == "Ilex montana"){
    taxon_pft_lookup$pft[i] = "???"          ???
    taxon_pft_lookup$commonName[i] = "mountain holly"}

  else if(genusSpecies == "Ilex opaca"){
    taxon_pft_lookup$pft[i] = "woody_shrub"   ???      # broadleaved evergreen tree
    taxon_pft_lookup$commonName[i] = "American holly"}

@@

@@

  else if(genusSpecies == "Mangifera indica"){
    taxon_pft_lookup$pft[i] = "???"       ???   # broadleaf evergreen tree
    taxon_pft_lookup$commonName[i] = "mango"}

@@

@@

  else if(genusSpecies == "Rhamnus davurica"){
    taxon_pft_lookup$pft[i] = "???"              ???
    taxon_pft_lookup$commonName[i] = "Dahurian buckthorn"}

@@

  else if(genusSpecies == "Prunus serotina"){
    taxon_pft_lookup$pft[i] = "???"       ???
    taxon_pft_lookup$commonName[i] = "black cherry"}

>>>>

```{r message=FALSE}
library(tidyverse)
library(here)
library(dplyr)
```

@@

```{r}
# list unique taxon labels, add an empty columns to fill with plant functional type (PFT) and common name labels.
# PFTs of interest: coniferous_forest, deciduous_forest, woody_shrub, grass_herb, and bare_ground.
taxon_pft_lookup <- data.frame(genusSpecies = unique(cleaned_spectra$genusSpecies),
                               commonName = NA,
                               pft = NA) %>% 
  # arrange alphabetically
  dplyr::arrange(genusSpecies)

@@

  else if(genusSpecies == "Acer circinatum"){
    taxon_pft_lookup$pft[i] = "???" # ???
    taxon_pft_lookup$commonName[i] = "vine maple"}

@@

  else if(genusSpecies == "Amelanchier laevis"){
    taxon_pft_lookup$pft[i] = "???" # ???
    taxon_pft_lookup$commonName[i] = "Allegheny serviceberry"}

  else if(genusSpecies == "Amyris elemifera"){
    taxon_pft_lookup$pft[i] = "???"     # ???
    taxon_pft_lookup$commonName[i] = "sea torchwood"}

@@

  else if(genusSpecies == "Bourreria sp."){
    taxon_pft_lookup$pft[i] = "???"   # ???
    taxon_pft_lookup$commonName[i] = "strongbark"}

@@

  else if(genusSpecies == "Cercis canadensis"){
    taxon_pft_lookup$pft[i] = "???"   # ???
    taxon_pft_lookup$commonName[i] = "eastern redbud"}

@@

  else if(genusSpecies == "Cornus drummondii"){
    taxon_pft_lookup$pft[i] = "???"    # ???
    taxon_pft_lookup$commonName[i] = "roughleaf dogwood"}

  else if(genusSpecies == "Cornus florida"){
    taxon_pft_lookup$pft[i] = "???"    # ???
    taxon_pft_lookup$commonName[i] = "flowering dogwood"}

@@

  else if(genusSpecies == "Frangula purshiana"){
    taxon_pft_lookup$pft[i] = "???"     # ???
    taxon_pft_lookup$commonName[i] = "Cascara buckthorn"}

@@

  else if(genusSpecies == "Ilex montana"){
    taxon_pft_lookup$pft[i] = "???"          # ???
    taxon_pft_lookup$commonName[i] = "mountain holly"}

  else if(genusSpecies == "Ilex opaca"){
    taxon_pft_lookup$pft[i] = "woody_shrub"   # ???      # broadleaved evergreen tree
    taxon_pft_lookup$commonName[i] = "American holly"}

@@

 else if(genusSpecies == "Magnolia sp."){
    taxon_pft_lookup$pft[i] = "???"
    taxon_pft_lookup$commonName[i] = "magnolia"}

@@

  else if(genusSpecies == "Mangifera indica"){
    taxon_pft_lookup$pft[i] = "???"       # ???   # broadleaf evergreen tree
    taxon_pft_lookup$commonName[i] = "mango"}

@@

  else if(genusSpecies == "Oxydendrum sp."){
    taxon_pft_lookup$pft[i] = "deciduous_forest"
    taxon_pft_lookup$commonName[i] = "sourwood"}

  else if(genusSpecies == "Picea engelmannii"){
    taxon_pft_lookup$pft[i] = "coniferous_forest"
    taxon_pft_lookup$commonName[i] = "Engelmann spruce"}

  else if(genusSpecies == "Pinus contorta"){
    taxon_pft_lookup$pft[i] = "coniferous_forest"
    taxon_pft_lookup$commonName[i] = "lodgepole pine"}

  else if(genusSpecies == "Pinus echinata"){
    taxon_pft_lookup$pft[i] = "coniferous_forest"
    taxon_pft_lookup$commonName[i] = "shortleaf pine"}

  else if(genusSpecies == "Pinus flexilis"){
    taxon_pft_lookup$pft[i] = "coniferous_forest"
    taxon_pft_lookup$commonName[i] = "limber pine"}

  else if(genusSpecies == "Pinus palustris"){
    taxon_pft_lookup$pft[i] = "coniferous_forest"
    taxon_pft_lookup$commonName[i] = "longleaf pine"}

  else if(genusSpecies == "Pinus ponderosa"){
    taxon_pft_lookup$pft[i] = "coniferous_forest"
    taxon_pft_lookup$commonName[i] = "ponderosa pine"}

  else if(genusSpecies == "Pinus sp."){
    taxon_pft_lookup$pft[i] = "coniferous_forest"
    taxon_pft_lookup$commonName[i] = "pine"}

  else if(genusSpecies == "Pinus taeda"){
    taxon_pft_lookup$pft[i] = "coniferous_forest"
    taxon_pft_lookup$commonName[i] = "loblolly pine"}

@@

  else if(genusSpecies == "Rhamnus davurica"){
    taxon_pft_lookup$pft[i] = "???"              # ???
    taxon_pft_lookup$commonName[i] = "Dahurian buckthorn"}

@@

  else if(genusSpecies == "Prunus serotina"){
    taxon_pft_lookup$pft[i] = "???"       # ???
    taxon_pft_lookup$commonName[i] = "black cherry"}
